---
title: 'Module 5 Assignment: Forecasting Demand for Shoe Laces and Blouses'
author: "Yi Ding"
output:
  html_document:
    df_print: paged
---


## Load Library
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(tidymodels)
library(janitor)
library(skimr)
library(kableExtra)
library(GGally)
library(vip)        
library(fastshap)   
library(MASS)
library(ISLR)
library(tree)
library(ggplot2)
library(dplyr)
library(lubridate)
library(imputeTS)
library(imputeTS)
library(forecast)
library(urca)
library(pracma)
library(fpp2)
library(forecast)
```


## Import Data
```{r}
sales <- read_csv("RetailSales2.csv") %>% clean_names()
head(sales)
```


## Create Time Series Objects & Exploratory Graphs
```{r}
# -- time series for laces
laces <- subset(sales, select = c(laces))
laces_ts <- ts(laces, start = c(1994,1), frequency = 12)
plot(laces_ts)
ggAcf(laces_ts)
ggPacf(laces_ts)

# -- time series for blouses
blouses <- subset(sales, select = c(blouses))
blouses_ts <- ts(blouses, start = c(1994,1), frequency = 12)
plot(blouses_ts)
ggAcf(blouses_ts)
ggPacf(blouses_ts)
```


## Forecasting Demand for Laces

## Fit SES Model
```{r}
laces_ses <- ses(laces_ts, h=3)
summary(laces_ses)
checkresiduals(laces_ses)

forecast(laces_ses)
laces_ses %>% forecast() %>% autoplot()
```


## Try Holt Winters to Incorporate Seasonality
```{r}
laces_hw <- hw(laces_ts, seasonal = "additive", h=3)
summary(laces_hw)
checkresiduals(laces_hw)

laces_hw %>% forecast() %>% autoplot()
```


## Fit Seasonal Exponential Smoothing Model
```{r}
laces_ets <- ets(laces_ts, model = "ZNZ")
summary(laces_ets)
checkresiduals(laces_ets)

forecast(laces_ets, h=3)

laces_ets %>% forecast() %>% autoplot()
```


## Compare to auto.arima
```{r}
fit_laces_auto <- auto.arima(laces_ts)
summary(fit_laces_auto)
checkresiduals(fit_laces_auto)
accuracy(fit_laces_auto)

forecast(fit_laces_auto, h=3)
fit_laces_auto %>% forecast() %>% autoplot()
```


## Forecasting Demand for Blouses

## Fit SES Model
```{r}
blouses_ses <- ses(blouses_ts, h=3)
summary(blouses_ses)
checkresiduals(blouses_ses)

forecast(blouses_ses)
blouses_ses %>% forecast() %>% autoplot()
```


## Try Holt Winters to Incorporate Trend and Seasonality
```{r}
# -- additive
blouses_hwA <- hw(blouses_ts, seasonal = "additive", h=3)
summary(blouses_hwA)
checkresiduals(blouses_hwA)

blouses_hwA %>% forecast() %>% autoplot()

# -- multiplicative
blouses_hwM <- hw(blouses_ts, seasonal = "multiplicative", h=3)
summary(blouses_hwM)
checkresiduals(blouses_hwM)

blouses_hwM %>% forecast() %>% autoplot()
```


## Fit Seasonal Exponential Smoothing Model
```{r}
blouses_ets <- ets(blouses_ts, model = "ZZZ")
summary(blouses_ets)
checkresiduals(blouses_ets)

forecast(blouses_ets, h=3)

blouses_ets %>% forecast() %>% autoplot()
```


## Compare to auto.arima
```{r}
fit_blouses_auto <- auto.arima(blouses_ts)
summary(fit_blouses_auto)
checkresiduals(fit_blouses_auto)
accuracy(fit_blouses_auto)

forecast(fit_blouses_auto, h=3)

fit_blouses_auto %>% forecast() %>% autoplot()
```

